Online {\IterComp}

### 2017-09-15 prof.tex
minor in prof

In contrast to the na\"ive instrumentation where each basic block records only its own amount of work, with the optimal profiling the work
counter increments needs to take other basic blocks into account. Figure~\ref{fig:cfg-example} shows an example CFG, where the instrumented
blocks are marked with red. In this example, executing block $B_5$ implies not executing $B_6$. To compute the amount of work associated
with each instrumentation probe, we first need to determine how reaching a probe relates with executing or not a basic block. Starting from
instrumented edges, we build symbolic expressions for each edge of their frequency counts as a linear function of probe counts, as seen in
Figure~\ref{fig:cfg-example}. If a symbolic expression for an edge and the corresponding block contains a positive term for a probe, this
means that the block is executed when we reach the probe, so the block's cost should be added at that probe. Conversely, if the expression
contains a negative term for a probe, then the block is executed when we do not reach the probe, so the block's cost should be subtracted.
In our example CFG, the symbolic expression for the basic block $B_8$ is $P_0 - P_1$, so the amount of work of $B_8$, denoted by $w(B_8)$,
is incremented in probe $P_0$ and decremented in $P_1$.

>>>>

In contrast to the na\"ive instrumentation where each basic block records only its own amount of work, with the optimal profiling the work
counter increments need to take other basic blocks into account. Figure~\ref{fig:cfg-example} shows an example CFG, where the instrumented
blocks are marked with red. In this example, reaching probe $P_2$ implies not only executing block $B_5$ but also not executing $B_6$.

To compute the amount of work associated
with each instrumentation probe, we first need to determine how reaching a probe relates with executing or not a basic block. Starting from
instrumented edges, we build symbolic expressions for each edge of their frequency counts as a linear function of probe counts, as seen in
Figure~\ref{fig:cfg-example}. If a symbolic expression for an edge and the corresponding block contains a positive term for a probe, this
means that the block is executed when we reach the probe, so the block's cost should be added at that probe. Conversely, if the expression
contains a negative term for a probe, then the block is executed when we do not reach the probe, so the block's cost should be subtracted.
In our example CFG, the symbolic expression for the basic block $B_8$ is $P_0 - P_1$, so the amount of work of $B_8$, denoted by $w(B_8)$,
is incremented in probe $P_0$ and decremented in $P_1$.
